---
title: "Exploratory Data Analysis"
subtitle: "UBC R Study Group"
output: ioslides_presentation
author: "Aaron Quinton"
date: "Oct. 31, 2018"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Acknowledgements

- Online Text *R for Data Science* by Garrett Grolemund & Hadley Wickham  
[R for Data Science Ch. 7 - EDA](https://r4ds.had.co.nz/exploratory-data-analysis.html)

- The *Hass Avocado Board* and Justin Kiggins for compiling Avacado data  
[Dataset csv download link on Kaggle](https://www.kaggle.com/neuromusic/avocado-prices/home)


## Intro to Exploratory Data Analysis (EDA)

EDA is a creative process with the purpose of **exploring** your data to generate quality questions. It is not quantitative but more qualitative in nature.

>“There are no routine statistical questions, only questionable statistical routines.” — Sir David Cox  

A good starting place for questions:  

 - What type of variation occurs within my variables?  
 - What type of covariation occurs between my variables?

To answer these question its crucial to know if our data is Categorical or Numerical.

## Before Getting Our Hands Dirty

**Finding Data**

- [Google Dataset Tool Search](https://toolbox.google.com/datasetsearch)
- [Kaggle Datasets](https://www.kaggle.com/datasets)
- [Awesome-Public-Dataset Repo](https://github.com/awesomedata/awesome-public-datasets)
- Built in R Datasets or Dataset packages on CRAN. To see the list type `data()` in console
  
  
  
```{r cars, echo = TRUE}
summary(cars)
```
